### 2013-08-22 doc/dissertation/document/frontmatter/abstract.tex
cleaning up some whitespace to reduce the length

First, solutions to the $SP_N$ discretization of the linear Boltzmann
neutron transport equation are obtained using MCSA with a difficult
criticality calculation for a light water reactor fuel assembly used
as the driving problem. It was discovered that basic Jacobi-based
preconditioning as used in previous work was not sufficient to achieve
convergence due to the dominating effect of the light water
moderator. To enable MCSA as a solution technique a group of modern
preconditioning strategies are researched. The new preconditioning
techniques, however, create unwanted growth in both memory consumption
and computation time for these problems. MCSA was verified to produce
the correct solution for the fuel assembly criticality problem when
compared to conventional Krylov methods and demonstrated improved
iterative performance over GMRES by converging in fewer iterations
when using the same preconditioning.

Second, solutions to the compressibleNavier-Stokes equations were
obtained by developing the Forward-Automated Newton-MCSA (FANM) method
for nonlinear systems based on Newton's method. Three difficult fluid
benchmark problems in both convective and driven flow regimes were
used to drive the research and development of the method. It was found
for all benchmarks that FANM produced identical solutions when
compared to those generated by modern Newton-Krylov methods. For each
benchmark, performance comparisons between FANM and Newton-Krylov were
also conducted. For 8 out of 12 benchmark cases, it was found that
FANM had better iterative performance than the Newton-Krylov method by
converging the nonlinear residual in fewer linear solver iterations
with the same preconditioning.

>>>>

First, solutions to the $SP_N$ discretization of the linear Boltzmann
neutron transport equation are obtained using MCSA with a difficult
criticality calculation for a light water reactor fuel assembly used
as the driving problem. It was discovered that basic Jacobi-based
preconditioning as used in previous work was not sufficient to achieve
convergence due to the dominating effect of the light water
moderator. To enable MCSA as a solution technique a group of modern
preconditioning strategies are researched. MCSA was verified to
produce the correct solution for the fuel assembly criticality problem
when compared to conventional Krylov methods and demonstrated improved
iterative performance over GMRES by converging in fewer iterations
when using the same preconditioning. The new preconditioning
techniques, however, create unwanted growth in both memory consumption
and computation time for these problems.

Second, solutions to the compressible Navier-Stokes equations were
obtained by developing the Forward-Automated Newton-MCSA (FANM) method
for nonlinear systems based on Newton's method. Three difficult fluid
benchmark problems in both convective and driven flow regimes were
used to drive the research and development of the method. It was found
for all benchmarks that FANM produced identical solutions when
compared to those generated by modern Newton-Krylov methods. For each
benchmark, performance comparisons between FANM and Newton-Krylov were
also conducted. For 8 out of 12 benchmark cases, it was found that
FANM had better iterative performance than the Newton-Krylov method by
converging the nonlinear residual in fewer linear solver iterations
with the same preconditioning.
